---
title: "Association Analysis in R"
author: "Jianqi Huang"
katex: true
date: '2022-10-03'
output: html_document
---

### loading packages
```{r,echo=TRUE,results='hide'}
rm(list = ls())
library("RColorBrewer")
library("arules")
library("arulesViz")
```

### Create transaction data and mine association rules

```{r}
a_list <- list(
  c("m","o","n","k","e","y"),
  c("d","o","n","k","e","y"),
  c("m","a","k","e"),
  c("m","u","c","k","y"),
  c("c","o","o","k","i","e")
)
```

### Set transaction names

```{r,echo=TRUE}
names(a_list) <- paste("Tr",c(1:5), sep = "")
a_list
```

### Use the constructor to create transactions

```{r,echo=TRUE,message=FALSE}
trans1 <- transactions(a_list)
trans1
```

### set the parameter(includes support and confidence but not lift) to find out the frequency itemset and rule

```{r,echo=TRUE,results='hide'}
frequency_rules<-apriori(trans1,parameter = list(supp = 0.6, target = "rules"))

rules <- apriori(trans1,parameter = list(supp = 0.6, conf = 0.8, target = "rules",minlen=2))
```

### frequency itemset table output(not strictly)

```{r,echo=TRUE}
inspectDT(frequency_rules)
arules::itemFrequencyPlot(trans1, topN = 20,
                          main = 'Relative Item Frequency Plot',
                          col = brewer.pal(8,'Pastel2'),
                          type ="absolute",
                          ylab = "Item Frequency (Relative)")
```

### rule table output

```{r,echo=TRUE}
inspectDT(rules)
```

### data visualization

```{r,echo=TRUE}
plot(rules, method = "graph",  engine = "htmlwidget")
plot(rules, method="paracoord")
```

### summary for the rules and conclusion

```{r,echo=TRUE}
summary(rules)
```
