---
title: "How to use mermaid in Rmd"
date: 2022-11-03
author: Jianqi Huang
---

## Introduction

`mermaid` is a useful plugin in diagramming and charting tool in markdown to create and modify diagrams dynamically based on JavaScript.


```{r,fig.width=50}
library(DiagrammeR)
g  <- mermaid("
graph LR
    A-->B;B-->C;C-->F;F-->A")
g
```


some is different with mermaid in markdown that we need to construct the relationship from 'A' to 'B' to 'C' by the program with two lines.But we could complete in `markdown` in one line 
`a-->b-->c`

```{r}
g<-DiagrammeR("
graph LR
  a==>b{that me think}
  a==>d
  b==>text
  text==>c
")
g
```
- Note:we use the function `DiagrammeR` or `mermaid` is the same

## Node Shape and Text
the basic grammar is `[ID][opening brace][label][closing brace]
`

- `id1{rhomb}`
- `id2(round retangle)`
-	`id3[retangle]`

- `id4((circular))`
-	`id5>flag]`

```{r}
mermaid("
graph TD
  A{node text1}
  B(node text2)
  C((note text3))
  D[note text4]
  E>note text5]
")
```

## Defining a graph

- `graph LR`: left to right
- `graph RL`: right to left
- `graph TB`: top to bottom
- `graph BT`: bottom to top
- `graph TD`: top down (same as TB)



## Other setting

- arrow and no arrow:'-->' and '---' ,the no arrow is different from mermaid in markdown that '--'.
- dotted line: `-.-`
- adding text: just add a dot `.` before the text
- bold arrow: `==>`

```{r}
DiagrammeR("
  graph TB
    a-.->b
    b---tx
    tx==>c
  ")
```


## adding color and border
`stlye [ID] fill:[color_numver],stroke:[border_number]`
```{r}
DiagrammeR("
graph LR
  A(Rounded)-->B[Squared];
  B-->C{A Decision};
  C-->D[Square One];
  C-->E[Square Two];
  style A fill:#E5E25F,stroke:#334;
  style B fill:#87AB51,stroke:#333; 
  style C fill:#3C8937;
  style D fill:#23772C; 
  style E fill:#B6E6E6;"
)
```

  

## Text in the arrow

```{r}
mermaid(
"   graph LR
    A[Hard edge] -->|Link text| B(Round edge)
    B --> C{Decision} 
    C -->|One| D[Result one]
    C -->|Two| E[Result two]
    ")
```

## Mermaid sequence diagrams
we could draw a sequence diagram using 'sequenceDiagram'. Next to describe the relationship from an attribute to another.
```{r}
DiagrammeR("
 sequenceDiagram;
    customer->>ticket seller: ask for a ticket;
    ticket seller->>database: seats;
    alt tickets available
      database->>ticket seller: ok;
      ticket seller->>customer: confirm;
      customer->>ticket seller: ok;
      ticket seller->>database: book a seat;
      ticket seller->>printer: print a ticket;
    else sold out
      database->>ticket seller: none left;
      ticket seller->>customer: sorry;
    end
")
```

That may be useful when doing project management

## Source
- https://mermaid-js.github.io/mermaid/#/
- https://rich-iannone.github.io/DiagrammeR/graphviz_and_mermaid.html