---
title: Compare R Python and Julia
author: "jianqi"
date: "2022-10-25"
output: html_document

---
loading the package `JuliaCall`
```{r}
library(JuliaCall)
```

## python
```{python}
def test(x,y):
  if x<y:
    relation = "less than"
  elif x==y:
    relation = "equal to"
  else:
    relation = "great than"
  print("x is ", relation," y.")
#invoking test funtion
test(2,1)
````

## R 
```{r}
test<-function(x,y){
  if(x<y){
    relations = "less than"
  }
  if(x==y){
    relations = "equal to"
  }
  else{
    relations = "great than"
  }
  print(paste(x,"is",relations,y,"."))
}
#invoking test funtion
test(2,1)
```


## Julia
```{julia}
function test(x,y)
           if x < y
               relation = "less than"
           elseif x == y
               relation = "equal to"
           else
               relation = "greater than"
           end
           println("x is ", relation, " y.")
       end
test(2, 1)
```

comparing the function in different language, we clearly find that the in Julia is the simplest syntax. It does not use `{}` or `:` but also need to align in arrangement. 

- the if-else grammar, Different language inherit the syntax in function. the implement of `if` syntax in `R` is more like a function and python and Julia are more like a separate syntax.

- the syntax in logical comparison are same. `==` and `<=` etc. 

- python grammar habit：`object.method(other parameter)`

- R grammar habit：`method(object，other parameter)`




